---
title: "Finding Clusters"
author: "Randy Jacobus"
date: "July 5, 2014"
output: html_document

Produce three sets of random numbers so we can test our cluster finding techniques.

How do we produce the three sets?

```{r}
## Load libraries
library(ggplot2)
## Generate 3 sets of random numbers with different centers and name them
groups<-1:3
elements<-100
concentration<-50
xmean<-c(1,1.5,2)
ymean<-c(1,2,1)
xstd<-.25
ystd<-.25
xstdconc<-.05
ystdconc<-.05

data<-data.frame()
for  (i in 1:length(groups)) {
     group<-rep(groups[i],elements)
     groupconc<-rep(groups[i],concentration)
     
     set.seed(1)
     xcoord<-rnorm(xmean[i],xstd,n=elements)
     ycoord<-rnorm(ymean[i],ystd,n=elements)
     temp<-data.frame(cbind(group,xcoord,ycoord))
     
     xcoord<-rnorm(xmean[i],xstdconc,n=concentration)
     ycoord<-rnorm(ymean[i],ystdconc,n=concentration)
     temp2<-data.frame(cbind(group=groupconc,xcoord,ycoord)) 
     
     temp3<-data.frame(rbind(temp,temp2))
     
     data<-data.frame(rbind(data,temp3)) 
 }
```

Plot this random set of numbers.

How do we plot?

```{r, echo=FALSE}
## Graph this dataframe using a different colors for each group.
myplot<- ggplot(data, aes(x = xcoord, y = ycoord, colour = group)) +
  geom_point()
  print(myplot)
```

How do we define a cluster?

What techniques are there to find clusters?

Which one do we like and why?

```{r}

```

Lets plot the cluster?

```{r, echo=FALSE}

```

How does this compare to the standard methods of finding clusters?

K Means?




















Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
